Fast and Flexible Binary Instrumentation for the Kernel

### 2013-12-05 VEE-14/paper.tex
Updated the intro.

@@

Instrumenting all code (e.g., the whole kernel) imposes unnecessary performance overheads when only a subset of the code is being analyzed (e.g., modules, functions). In practice, we would like to target instrumentation at specific code for efficiency, while also allowing rich and detailed instrumentation of the targeted code. Limiting the scope of what is instrumented is  important because the overhead introduced by using runtime code instrumentation is usually dominated by the instrumentation itself and not the runtime system supporting that instrumentation.

@@

Another limitation of existing systems is that they are unable to perform efficient runtime code specialization, i.e. they are unable to change how code is instrumented based on the context in which that code will run. For example, Granary's Read-Copy-Update (RCU) debugging tool, \texttt{RCUdbg}, specializes instrumentation at different stages of use of the RCU synchronization API. Correct usage of the RCU API allows programmers to create scalable, shared data structures that permit concurrent access and modification. The ``trick" of RCU is that readers might not see the latest write to the data structure, and writers must synchronize to modify the data structure. \texttt{RCUdbg} distinguishes between code executing inside \emph{read-side} and \emph{write-side} critical sections, and instruments each code context differently. In read-side critical sections, \texttt{RCUdbg} detects bugs when readers access potentially non-existent data, do not the correct accessor API, or attempt to write to shared data. In write-side critical sections, \texttt{RCUdbg} detects when writers write to shared data without using the correct API.

%In reader-side code

%For example, Granary has a tool that  dynamically constructs inter- and intra-procedural control flow graphs (CFGs). The outputs of this tool enable Granary to do better runtime register allocation, which improves tool efficiency. Part of building CFGs requires tracking whether or not a given basic block is the entrypoint to a function. This is challenging with existing DBT systems because some optimized functions will re-execute their first basic block, which might incorrectly appear as new function calls in the CFGs. Granary solves this problem using demand-based runtime code specialization: every entrypoint basic block is instrumented in one way, and later re-executions of any entrypoint basic blocks are specialized and instrumented in another way.

The \texttt{RCUdbg} tool is an example of \emph{context-driven code specialization}: code executing inside of a read-side critical section is instrumented differently from code executing inside of a write-side critical section, and code execution outside of both contexts executes with minimal instrumentation. In a Granary tool, each tracked execution context is associated with its own instrumentation policy. An instrumentation policy decides how to instrument code that will execute within the associated context. Granary is able to track execution contexts because it explicitly maintains policy information in translated basic blocks. This avoids typical poblems with tracking context in just-in-time DBT systems (e.g., maintaining runtime context-tracking state, reentrancy, and the inability to predict later execution contexts at translation time).

@@

The rest of the paper describes Granary in more detail. \Cref{sec:dbt} describes how Granary is implemented.

@@

@@

%, but introduces implementation complexities and high overheads for interrupt-heavy workloads. Precise interrupt delivery is one of the ways which DRK maintains transparency: interrupt handlers only 
%The interaction between DRK's interrupt delaying mechanism and how also makes designing instrumentation subtlely harder. For example, Granary's \texttt{RCUdbg} tool injects instrumentation inside of read-side critical sections that looks for loads/stores from tainted addresses. When necessary, \texttt{RCUdbg} spills and restores registers around each checked load/store operation, so that the registers can be safely used by the checking code. This is an examuple of pre and post instruction instrumentation: some instructions are injected before a native instruction, and some instructions are injected after. DRK is oblivious to the relationship between pre/post instrumentation, and so an interrupt that occurs within the pre-instrumentation will only be delayed until the native instruction.

@@

Granary gives tools the ability to be selective about what is instrumented. A natural extension of this selectivity is to allow tools to specialize how code is instrumented by dynamically switching the policy used to instrument code. Specialization is desirable in several cases. For example, some instrumentation is high-overhead, but does not need to be applied to all code. One example of this is Granary's \texttt{RCUdbg} tool, which instruments read-side and write-side critical sections more heavily than the rest of code. Unfortunately, existing DBT systems fall short in their support for runtime code specialization \cite{DRK,btkernel,Pin,DynamoRIO}.

To implement the equivalent of \texttt{RCUdbg}'s runtime code specialization using an existing DBT system requires that a tool developer maintain, update, and check runtime state to know whether or not code is executing inside or outside of a read-side critical section. If a basic block is executing in a read-side critical section, then instrumentation should be enabled, and if it's not in a read-side critical section then it should be disabled. Enabling/disabling instrumentation might be done at the instruction granularity, which introduces at least one branch instruction per native instruction, or at the granularity of basic blocks, which requires generating two copies of each native basic block, where a single branch at the beginning of a basic block chooses between the instrumented or uninstrumented version. Up until now, it has been assumed that there is a mechanism for maintaing state that consistently tracks the current execution context of kernel code (inside vs. outside of a read-side critical section). However, maintaining state in a way that is reentrant and resilient again arbitrary pre-emption and resumption is onerous.

@@

%For example, instrumenting only module code allows Granary to specialize the execution of native code. In the same way, policy switching allows Granary's \texttt{RCUdbg} tool to specialize the execution of instrumented code executing inside of read-side and write-side critical sections. In fact, optimizing the performance of an early Granary tool was the original motivation for policy switching.

@@

%In the case of our \texttt{RCUdbg}, there were three execution contexts: within and outside of a read-side critical section. If the same module basic block is  executed in the two contexts, then Granary's code cache would contain two different instrumented versions of that basic block. The way that Granary distinguishes between different execution contexts is with \emph{instrumentation policies}.

@@

For example, our \texttt{RCUdbg} invokes a policy switch from policy $P_{\mathit{null}}$ to policy $P_{\mathit{read\_critical}}$ when $P_{\mathit{null}}$'s instrumentation function observes a \texttt{call} instruction to the \texttt{rcu\_read\_lock} Linux kernel function. A similar switch occurs from $P_{\mathit{read\_critical}}$ back to $P_{\mathit{null}}$ at a \texttt{rcu\_read\_unlock}. Specialization that distinguishes between the inside and outside of read-side critical sections allows \texttt{RCUdbg} to do heavy-weight checks on functions like \texttt{memset}, but only when \texttt{memset} is invoked from within a read-side critical section.

Because policies name an execution context, they also represent states in a finite state machine. That is, code cache execution is in the state named by a policy if the  executing code was instrumented by that policy. A state transition occurs when control transfers from code instrumented by one policy to code instrumented by another policy. A limitation with this approach is that a single state does not encode the sequence of previous states that led to execution being in the current state. For example, RCU permits nested read-side critical sections. If two read-side critical sections are nested then switching from $P_{\mathit{read\_critical}}$ to $P_{\mathit{null}}$ on the first \texttt{call} to \texttt{rcu\_read\_unlock} meant that our tool would lose track of being in the context of the outer read-side critical section.  \texttt{RCUdbg} solves this problem by tracking the nesting depth of RCU read-side critical sections using policies, e.g. $P_{\mathit{read\_critical}_1}$, $P_{\mathit{read\_critical}_2}$, etc.

@@

\section{Application: RCUdbg}

@@

Granary's \texttt{RCUdbg} tool is designed to catch RCU bugs related to kernel code misusing pointers to RCU-protected data structures. The following is a non-exhaustive list of requirements that must be met by reader and writer threads operating on an RCU-protected data structure. The list omits a description of how RCU-protected data structures are garbage collected, which is beyond the scope of the bugs caught by \texttt{RCUdbg}.

@@

\texttt{RCUdbg} is primarily concerned with finding bugs related to RCU-rpotected pointer misuses by reader threads (both inside and outside of read-side critical sections). As mentioned above, RCU bugs sometimes manifest as use-after-free bugs. Unfortunately, a pure use-after-free-based checking approach is insufficient (\Cref{fig:rcu_assign_bug} is one such example). \Cref{fig:rcu_existence_bug} is an example of an RCU usage bug that can manifest as a use-after-free bug if one is unlucky enough to observe a very specific thread schedule. Suppose that execution is interrupted after \texttt{rcu\_read\_unlock}, but before the access to \texttt{elm->data}. If \texttt{elm} is garbage collected and freed before the code resumes its execution, then the access to \texttt{elm->data} is a use-after-free bug. This kind of bug is a time bomb waiting to go off. Fortunately, \texttt{RCUdbg} catches the bug in \Cref{fig:rcu_existence_bug} right when \texttt{elm->data} is accessed.

@@

\texttt{RCUdbg} detects the the following RCU bugs related to misuses of RCU-protected pointers.
\begin{itemize}[leftmargin=3.2em]
	\item[B1)] Reads through an RCU-dereferenced pointer outside of a read-side critical section (\Cref{fig:rcu_existence_bug}).
	\item[B2)] Reads through an RCU-dereferenced pointer in the wrong read-side critical section.

@@

\texttt{RCUdbg} gains visibility on RCU operations in two ways: \begin{enumerate}
	\item The Linux kernel RCU implementation is annotated to provide more information to \texttt{RCUdbg}. This information includes source code file and line information for bug reporting, and additional memory references that \texttt{RCUdbg} uses to get better visibility on bugs. These annotations are strictly internal to the RCU API, and thus require no changes to code using this API.
	\item The annotated RCU API functions are specialized using Granary's function wrapping feature (\Cref{sec:function_wrapper}). Specifically, 
\end{enumerate}

%\texttt{RCUdbg} interposes on an annotations are added into the Linux kernel's RCU implementation. These annotations

>>>>

% For writing Granary tool names.
\newcommand{\toolname}[1]{{\scshape #1}}

@@

Instrumenting all code (e.g., the whole kernel) imposes unnecessary performance overheads when only a subset of the code is being analyzed (e.g., modules, functions). In practice, we would like to target instrumentation at specific code for efficiency, while also allowing rich and detailed instrumentation of the targeted code. Limiting the scope of what is instrumented is  important because the overhead introduced by using runtime code instrumentation is usually dominated by the instrumentation itself and not the baseline overhead of the runtime system supporting that instrumentation. Also, specializing based on what is instrumented allows instrumentation tools to avoid unnecessary filtering. That is, if one wants to instrument RCU read-side and write-side critical sections, as is the case with Granary's \toolname{RCUdbg} tool, then instrumenting all code just to filter out / find those sections is wasteful.

@@

Another limitation of existing systems is that they are unable to perform efficient runtime code specialization, i.e. they are unable to change how code is instrumented based on the context in which that code will run. This is unfortunate because it means that tools wanting to instrument code differently must create their own solution that works around this deficiency of existing systems. A typical solution is for tools to generate as many instrumented versions of the code as there are execution contexts. When instrumented code is  executing, runtime checks query some thread-private or CPU-private state, and jump to the correct version of the code for the current context. Runtime checks of this form are inefficient, and generating many versions of the code introduces bloat. The machinery needed to multiplex between different versions of instrumented code is also orthogonal to the goals of the instrumentation tool, thus distracting tool-developers from their primary objectives.

%Using an existing system, 
% get around the problem of needing different instrumentation in different contexts, existing systems need to create as many versions of the code as there are contexts. Runtime checks must also be inserted into the code that coordinate with the runtime to track and detect the current execution context and jump to the correct version of the code. Runtime checks and state tracking impose unnecessary complications to tool-authors. The added code needed to query the current context and switch to a different version of the instrumentation is code that is not actively achieving the primary goal of the tool, and is instead making up for a defeciency in the runtime system.  
%are orthogonal to the main goals of an analysis tool:
% Aside from the additional ineffeciency of these runtime checks, there is also the 
% However, generating many differently instrumented versions of the code introduces bloat, especially when not all versions are well exercised. Also, generating many different versions of the code introduces state tracking and switching costs.
% This imposes unnecessary performance overheads because of the need to additional instrumentation that is unrelated to 
% due to having to perform runtime detection and swichting
% to the right version of the code for every basic block or every instruction.
% according to \emph{all} contexts. Instrumenting code according to all contexts imposes unnecessary performance overheads and requires state tracking.
%,  dynamically tracking the current context, and dynamically choosing which 
% commit to instrumenting code to handle \emph{all} contexts. For example, if

One example of a tool that uses runtime code specialization is Granary's Read-Copy-Update (RCU) debugging tool, \toolname{RCUdbg}. \toolname{RCUdbg} catches bugs related to invalid uses of RCU-protected pointers (\Cref{sec:rcudbg}). \toolname{RCUdbg} distinguishes between two kinds of RCU-protected pointers (reader-side and writer-side) and plain old pointers, and three execution contexts (inside of a read-side critical section, inside of a write-side critical section, and in non-RCU-related code). The actions taken when a pointer is de-referenced varies depending on the kind of pointer and the execution context. Code executing in read-side critical sections is specialized to enforce that only plain-old and read-side pointers are accessed, and that all accesses through read-side pointers are memory reads. Write-side critical sections are specialized in a similar way.

%There are similar checks for write-side pointers in write-side critical sections.
% The instrumentation performed inside of read- and write-side critical sections is heavy weight, while code running in the third execution context can either run with lightweight or no instrumentation.
%RCUdbg distinguishes between RCU-protected pointers and plain old pointers. There are two kinds of RCU-protected pointer (read-only, and read/write), and every access to an RCU-protected pointer is checked. The checks performed on an access to an RCU-protected pointer are context-specific. That is, a read-only pointer can only be read from within an RCU read-side critical section. Read/write pointers have similar restrictions. RCUdbg needs to know in which context some code is executing, i.e. in a read-side or write-side critical section, or outside of all critical section, and change instrumentation to check for different kinds of bugs based on the context.
%A read/write pointer has different restrictions. In read-side critical sections, a read/write pointer can only be accessed by means of a special API function. In write-side critical sections, a read/write pointer can only be written to 
% One kind of RCU-protected pointer can be read from within ``RCU read-side critical sections", while another kind can (almost) arbitrarily accessed, but only inside of an ``RCU write-side critical section". Outside of these two kinds of sections, accessing RCU-protected pointers is illegal. The distinction between different contexts of code (read-side, write-side, outside), and different kins of pointers makes
%Creating a tool to catch these kinds of bugs with an existing DBT system would be difficult because that tool would need to  
%For example, Granary's Read-Copy-Update (RCU) debugging tool, \toolname{RCUdbg}, specializes instrumentation at different stages of use of the RCU synchronization API. Correct usage of the RCU API allows programmers to create scalable, shared data structures that permit concurrent access and modification. The ``trick" of RCU is that readers might not see the latest write to the data structure, and writers must synchronize to modify the data structure. \toolname{RCUdbg} distinguishes between code executing inside \emph{read-side} and \emph{write-side} critical sections, and instruments each code context differently. In read-side critical sections, \toolname{RCUdbg} detects bugs when readers access potentially non-existent data, do not the correct accessor API, or attempt to write to shared data. In write-side critical sections, \toolname{RCUdbg} detects when writers write to shared data without using the correct API. 
%In reader-side code
%For example, Granary has a tool that  dynamically constructs inter- and intra-procedural control flow graphs (CFGs). The outputs of this tool enable Granary to do better runtime register allocation, which improves tool efficiency. Part of building CFGs requires tracking whether or not a given basic block is the entrypoint to a function. This is challenging with existing DBT systems because some optimized functions will re-execute their first basic block, which might incorrectly appear as new function calls in the CFGs. Granary solves this problem using demand-based runtime code specialization: every entrypoint basic block is instrumented in one way, and later re-executions of any entrypoint basic blocks are specialized and instrumented in another way.

The \toolname{RCUdbg} tool is an example of \emph{context-driven code specialization}: code executing inside of a read-side critical section is instrumented differently from code executing inside of a write-side critical section, and code executing outside of both contexts runs natively or with lightweight instrumentation. Achieving this level of specialization using and existing system requires complicated runtime state management and checks to switch between different versions of the code. With Granary, a tool like \toolname{RCUdbg} can specialize code using instrumentation policies. An instrumentation policy is a function that names an execution context and decides how to instrument instructions that will execute within that context. When a policy is used to instrument a sequence of instructions (called a basic block), a new version of the basic block is generated and cached.

\toolname{RCUdbg} defines three policies, and declares transitions between these policies when control flows in and out of RCU read- and write-side critical sections. When a function like \texttt{memset} is invoked in one context, the policy associated with that context is used to generate an instrumented version of \texttt{memset} for that context. If, for example, \texttt{memset} is never invoked within a read-side critical section, then \texttt{memset}'s code will never be specialized to perform the heavyweight checks needed to detect RCU-protected pointer misuses in this context. Similarly, if \texttt{memset} is executed both in a write-side critical section and outside of any RCU-related code, then two differently instrumented versions of \texttt{memset} will be generated.

The key insight of Granary's approach to runtime code specialization is that code versioning is a context-tracking mechanism. That is, if an instruction from a basic block instrumented by \toolname{RCUdbg}'s read-side critical section policy is being executed, then the current thread must be executing inside of a read-side critical section. Similarly, if the read-side policy is used to instrument a basic block, then \texttt{RCUdbg} knows at instrumentation time\footnote{Instrumentation time is analogous to ``compile time", in that a policy is generally used to instrument a basic block of code once, and then that basic block may be executed many times.} that this basic block will only execute within a read-side critical section. If the basic block contains a \texttt{call} to the \texttt{memset} function, then \texttt{memset} is also known to execute within a read-side critical section because it does not terminate a read-side critical section. By deciding which version of \texttt{memset} to execute at instrumentation time, \toolname{RCUdbg} avoids expensive runtime checks that other systems impose in order to achieve similar kinds of specialization. \toolname{RCUdbg} can specify that \texttt{memset} will also execute within a read-side critical section by telling Granary that it should use the read-side critical section policy to instrument \texttt{memset}.

%Granary records 
%Policy information is recorded inside of Granary's

% instruction by telling Granary what policy to use to instrument the code 
%, and when the \texttt{call} is eventually executed, 
%This simplifies tool creation becase 
%By propagating policy information through control-flow transferring instructions, 
%Therefore, we can know at translation and instrumentation time that
% No additional state needs to be maintained by \texttt{RCUdbg} to determine which version of the basic block to execute.
%Any control-flow instructions the transfer control to other basic blocks that aren't the \texttt{rcu\_read\_unlock} function must also 
%That is, the failure of existing systems is that they have no built-in support for maintaining multiple versions of code. Tools built on existing systems must emulate versioning by duplicating their instrumentation for each desired version, and add code that executes the right version at the right time.  
%, as would be done using existing systems, 
%What makes Granary's runtime code specialization efficient is that it ties into Granary's \texttt{just-in-time} instrumentation model. That is, Granary only instruments code that will execute. Code that never executes is neither translated nor instrumented. Also, only one version of a basic block is generated at a time. Therefore, even though \toolname{RCUdbg} defines three policies, only
%If some native code is about to execute, then Granary will only instrument it with the policy associated with 
%, and an instrumentation policy is only applied to code if that code will execute within the context associated with that context.
%defines three different instrumentation policies--one for each execution context--and declares switches 
% instrumentation policies to 
%only needs to define three instrumentation policies (one for each execution context), and declare 
%different versions of the code are generated \emph{just-in-time}. Therefore, if the \texttt{memset} function is never executed inside of a read-side critical section, then \texttt{memset}'s code will never be specialized to perform the heavyweight checks needed to detect RCU-protected pointer misuses in this context. Similarly, if \texttt{memset} is executed both in a write-side critical section and outside of any RCU-related code, then two differently instrumented versions of \texttt{memset} will be generated. 
%However, unlike other systems, no runtime check that chooses to dispatch to one version of \texttt{memset} or another depending on the runtime context. Instead, 
% if some code never executes in a particular context, then Granary will not generate an instrumented version of that code for that context.  The second benefit of this approach is that it is stateless, and requires no runtime checks to switch between different versions of the code depending on the execution context. 
%Granary tracks the current execution context with zero runtime overhead by 
%In a Granary tool, each tracked execution context is associated with its own instrumentation policy. An instrumentation policy decides how to instrument code that will execute within the associated context. 
%Different versions of the code are instrumented \emph{just-in-time}. That is, there will 
%Granary is able to track execution contexts because it explicitly maintains policy information in translated basic blocks. This avoids typical poblems with tracking context in just-in-time DBT systems (e.g., maintaining runtime context-tracking state, reentrancy, and the inability to predict later execution contexts at translation time).

@@

The rest of the paper describes Granary in more detail. \Cref{sec:dbt} describes how Granary is implemented, \Cref{sec:what} describes how Granary can specialize instrumentation

@@

\subsection{Basic Blocks}

@@

%, but introduces implementation complexities and high overheads for interrupt-heavy workloads. Precise interrupt delivery is one of the ways which DRK maintains transparency: interrupt handlers only 
%The interaction between DRK's interrupt delaying mechanism and how also makes designing instrumentation subtlely harder. For example, Granary's \toolname{RCUdbg} tool injects instrumentation inside of read-side critical sections that looks for loads/stores from tainted addresses. When necessary, \toolname{RCUdbg} spills and restores registers around each checked load/store operation, so that the registers can be safely used by the checking code. This is an examuple of pre and post instruction instrumentation: some instructions are injected before a native instruction, and some instructions are injected after. DRK is oblivious to the relationship between pre/post instrumentation, and so an interrupt that occurs within the pre-instrumentation will only be delayed until the native instruction.

@@

Granary gives tools the ability to be selective about what is instrumented. A natural extension of this selectivity is to allow tools to specialize how code is instrumented by dynamically switching the policy used to instrument code. Specialization is desirable in several cases. For example, some instrumentation is high-overhead, but does not need to be applied to all code. One example of this is Granary's \toolname{RCUdbg} tool, which instruments read-side and write-side critical sections more heavily than the rest of code. Unfortunately, existing DBT systems fall short in their support for runtime code specialization \cite{DRK,btkernel,Pin,DynamoRIO}.

To implement the equivalent of \toolname{RCUdbg}'s runtime code specialization using an existing DBT system requires that a tool developer maintain, update, and check runtime state to know whether or not code is executing inside or outside of a read-side critical section. If a basic block is executing in a read-side critical section, then instrumentation should be enabled, and if it's not in a read-side critical section then it should be disabled. Enabling/disabling instrumentation might be done at the instruction granularity, which introduces at least one branch instruction per native instruction, or at the granularity of basic blocks, which requires generating two copies of each native basic block, where a single branch at the beginning of a basic block chooses between the instrumented or uninstrumented version. Up until now, it has been assumed that there is a mechanism for maintaing state that consistently tracks the current execution context of kernel code (inside vs. outside of a read-side critical section). However, maintaining state in a way that is reentrant and resilient again arbitrary pre-emption and resumption is onerous.

@@

%For example, instrumenting only module code allows Granary to specialize the execution of native code. In the same way, policy switching allows Granary's \toolname{RCUdbg} tool to specialize the execution of instrumented code executing inside of read-side and write-side critical sections. In fact, optimizing the performance of an early Granary tool was the original motivation for policy switching.

@@

%In the case of our \toolname{RCUdbg}, there were three execution contexts: within and outside of a read-side critical section. If the same module basic block is  executed in the two contexts, then Granary's code cache would contain two different instrumented versions of that basic block. The way that Granary distinguishes between different execution contexts is with \emph{instrumentation policies}.

@@

For example, our \toolname{RCUdbg} invokes a policy switch from policy $P_{\mathit{null}}$ to policy $P_{\mathit{read\_critical}}$ when $P_{\mathit{null}}$'s instrumentation function observes a \texttt{call} instruction to the \texttt{rcu\_read\_lock} Linux kernel function. A similar switch occurs from $P_{\mathit{read\_critical}}$ back to $P_{\mathit{null}}$ at a \texttt{rcu\_read\_unlock}. Specialization that distinguishes between the inside and outside of read-side critical sections allows \toolname{RCUdbg} to do heavy-weight checks on functions like \texttt{memset}, but only when \texttt{memset} is invoked from within a read-side critical section.

Because policies name an execution context, they also represent states in a finite state machine. That is, code cache execution is in the state named by a policy if the  executing code was instrumented by that policy. A state transition occurs when control transfers from code instrumented by one policy to code instrumented by another policy. A limitation with this approach is that a single state does not encode the sequence of previous states that led to execution being in the current state. For example, RCU permits nested read-side critical sections. If two read-side critical sections are nested then switching from $P_{\mathit{read\_critical}}$ to $P_{\mathit{null}}$ on the first \texttt{call} to \texttt{rcu\_read\_unlock} meant that our tool would lose track of being in the context of the outer read-side critical section.  \toolname{RCUdbg} solves this problem by tracking the nesting depth of RCU read-side critical sections using policies, e.g. $P_{\mathit{read\_critical}_1}$, $P_{\mathit{read\_critical}_2}$, etc.

@@

\section{Application: RCUdbg}\label{sec:rcudbg}

@@

Granary's \toolname{RCUdbg} tool is designed to catch RCU bugs related to kernel code misusing pointers to RCU-protected data structures. The following is a non-exhaustive list of requirements that must be met by reader and writer threads operating on an RCU-protected data structure. The list omits a description of how RCU-protected data structures are garbage collected, which is beyond the scope of the bugs caught by \toolname{RCUdbg}.

@@

\toolname{RCUdbg} is primarily concerned with finding bugs related to RCU-rpotected pointer misuses by reader threads (both inside and outside of read-side critical sections). As mentioned above, RCU bugs sometimes manifest as use-after-free bugs. Unfortunately, a pure use-after-free-based checking approach is insufficient (\Cref{fig:rcu_assign_bug} is one such example). \Cref{fig:rcu_existence_bug} is an example of an RCU usage bug that can manifest as a use-after-free bug if one is unlucky enough to observe a very specific thread schedule. Suppose that execution is interrupted after \texttt{rcu\_read\_unlock}, but before the access to \texttt{elm->data}. If \texttt{elm} is garbage collected and freed before the code resumes its execution, then the access to \texttt{elm->data} is a use-after-free bug. This kind of bug is a time bomb waiting to go off. Fortunately, \toolname{RCUdbg} catches the bug in \Cref{fig:rcu_existence_bug} right when \texttt{elm->data} is accessed.

@@

\toolname{RCUdbg} detects the the following RCU bugs related to misuses of RCU-protected pointers.
\begin{itemize}[leftmargin=3.2em]
	\item[B1)] Reads through an RCU-dereferenced pointer outside of a read-side critical section (\Cref{fig:rcu_existence_bug}).
	\item[B2)] Reads through an RCU-dereferenced pointer in the wrong read-side critical section.

@@

\toolname{RCUdbg} gains visibility on RCU operations in two ways: \begin{enumerate}
	\item The Linux kernel RCU implementation is annotated to provide more information to \toolname{RCUdbg}. This information includes source code file and line information for bug reporting, and additional memory references that \toolname{RCUdbg} uses to get better visibility on bugs. These annotations are strictly internal to the RCU API, and thus require no changes to code using this API.
	\item The annotated RCU API functions are specialized using Granary's function wrapping feature (\Cref{sec:function_wrapper}). Specifically, 
\end{enumerate}

%\toolname{RCUdbg} interposes on an annotations are added into the Linux kernel's RCU implementation. These annotations
